---
title: "Teabag windspeeds"
format: html
editor: visual
---

# Background

## Motivation

Teabags have become an almost integral part of science (see [Keuskamp et al, 2013](https://besjournals.onlinelibrary.wiley.com/doi/10.1111/2041-210X.12097)). However, it remains elusive if they could serve for advanced meteorological measurements just as well as for decomposition experiments or keeping researchers awake during late-night working sessions. Here, we explore the use of standard teabags to measure wind speed in an extreme alpine environment.

## Methodology

\[some fancy summary here\]

# Workflow

## Setup

```{r}
#| label: setup
#| message: false
#| warning: false

# load pacman which provides wrappers for installing and loading packages
if(!require(pacman)) install.packages("pacman")
# load/install packages
pacman::p_load(tidyverse,
               tidylog,
               lubridate,
               skimr)
```

## Data wrangling

Let's get the data in here and fix the formats some variables:

```{r}
#| label: data-import-wrangling
teabags <- read_csv(file = "221115_teabag_windspeed_data.csv") |> 
  
  # format date column from dd/mm/yyyy to standard format yyyy-mm-dd
  mutate(date = lubridate::dmy(date)) |> 
  # convert location_no, replicate, topo, type to factors
  mutate(across(c(location_no, replicate, topo, type),
                as.factor))

# Convert distance to a more standard unit (1kf = 0.3m)
teabags$distance_m = teabags$distance_kf * 0.3

```

```{r}
#| label: check-data

glimpse(teabags)

```
